### 2023-01-31 paper-thesis/chapters/99-conclusion.tex
Clean up citations + other work

We have demonstrated that the Calculus of Constructions can be implemented concisely in Statix, by storing substitutions in the scope graph. We have also presented a few extensions to the Calculus of Constructions and discussed how they could be implemented.

>>>>

This thesis presents an implementation of a dependently typed language in Statix. Our aim was to anther the following research questions:

\paragraph{Can the Calculus of Constructions be implemented in Statix? (Chapter \ref{chap:baselang})}

\paragraph{We show the implementation is easily extendable (Chapter \ref{chap:bools})}

\paragraph{We show how to add inference to the implementation (Chapter \ref{ch:inference})}

\paragraph{We show how to add support for inductive datatypes to the implementation (Chapter \ref{ch:datatypes})}

\paragraph{We show how to add support for universes to the implementation (Chapter \ref{ch:universes})}

\section{Future Work}
